---
title: "Probability Theory"
---

# Assignment 1

The probability of two consecutive events is obtained by multiplying the probabilities.


$P(T \cap S) = 0.06$

$P(T \cap \overline{S})= 0.24$

$P(\overline{T} \cap S) = 0.42$

$P(\overline{T} \cap \overline{S}) = 0.28$

$P(T \cap S) + P(T \cap \overline{S}) + P(\overline{T} \cap S)+P(\overline{T} \cap \overline{S})=1$

```{r}
a<-0.3*0.2
b<-0.3*0.8

c<-0.7*0.6
d<-0.7*0.4

a
b
c
d

a+b+c+d
```

# Assignment 2
Percentage of customers using all three devices: $0.5\%$

Percentage of customers using at least two devices: $7.3\%+3.3\%+8.8\%+0.5\% = 19.9\%$

Percentage of users using only one device: $42\%+10\%+27.8\%=79.8\%$


```{r}
7.3+3.3+8.8+0.5 
42+10+27.8
```

# Assignment 3

These results show that in case the alarm is triggered, there is a possibility of about 19.8% that the product is flawless and a probability of 80.2% that the product is faulty.

```{r}
ba<-0.97
bna<-0.01
a<-0.04

nab<-(bna*(1-a))/((bna*(1-a))+(ba*(a)))
nab

ab<-(ba*a)/((ba*a)+(bna*(1-a)))
ab
```




